Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
more

An example of an inadmissible function set is
$\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$,
since the formula $\ltrue$ is (trivially) closed under function expansion with respect to this set,
and there is no model of $T$
satisfying $\con{f}$'s definition. A more subtle example is given by %the set 
\[\{ 
 \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ),\;
 \forallf{\con{g}} x.\;\, \lite\bigl( \con{f}( x ) \teq 5,\;
   \con{g}( x ) \teq \con{f}( x ),\,
   \con{g}( x ) \teq \con{g}( x ) + 1)
\}\]
While this set has a model where $\con f$ and $\con g$ are interpreted as the constant $5$, it is not admissible
since the formula $\con{f}( 0 ) \teq 4$ is closed under function expansion with respect to this set,
but there exists no interpretation satisfying both $\con{f}( 0 ) \teq 4$ and
$\con{g}$'s definition.

>>>>

An example of an inadmissible function set is
$\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$,
since the formula $\ltrue$ is (trivially) closed under function expansion with respect to this set,
and there is no model of $T$
satisfying $\con{f}$'s definition. A more subtle example is given by %the set 
\[\{ 
 \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ),\;
 \forallf{\con{g}} x.\;\, \lite\bigl( \con{f}( x ) \teq 5,\;
   \con{g}( x ) \teq \con{f}( x ),\,
   \con{g}( x ) \teq \con{g}( x ) + 1)
\}\]
While this set has a model where $\con f$ and $\con g$ are interpreted as the
constant $5$, it is not admissible since the formula $\con{f}( 0 ) \teq 4$ is
closed under function expansion with respect to this set and yet there exists
no interpretation satisfying both $\con{f}( 0 ) \teq 4$ and $\con{g}$'s
definition.
